Efficiently Handling Guards in the Low Level Design of RPython's Tracing JIT

### 2012-08-07 talk/vmil2012/paper.tex
urlify links, don't color them

@@

\title{Efficiently Handling Guards in the Low Level Design of RPython's tracing JIT}

@@

The results presented in this section are based on numbers gathered by running
a subset of the standard PyPy benchmarks. The PyPy benchmarks are used to
measure the performance of PyPy and are composed of a series of
micro-benchmarks and larger programs.\footnote{http://speed.pypy.org/} The
benchmarks were taken from the PyPy benchmarks repository using revision
\texttt{ff7b35837d0f}.\footnote{https://bitbucket.org/pypy/benchmarks/src/ff7b35837d0f}
The benchmarks were run on a version of PyPy based on the
tag~\texttt{0b77afaafdd0} and patched to collect additional data about the
guards in the machine code
backends.\footnote{https://bitbucket.org/pypy/pypy/src/0b77afaafdd0} All
benchmark data was collected on a MacBook Pro 64 bit running Max OS 10.8 with
the loop unrolling optimization disabled.\footnote{Since loop unrolling
duplicates the body of loops it would no longer be possible to meaningfully
compare the number of operations before and after optimization. Loop unrolling
is most effective for numeric kernels, so the benchmarks presented here are not
affected much by its absence.}

>>>>

\hypersetup{%
  plainpages=false,%
  %hyperfootnotes=false,%
  colorlinks=true,%
  urlcolor=black,%
  citecolor=black,%
  linkcolor=black,%
  pdftitle={Efficiently Handling Guards in the Low Level Design of RPython's Tracing JIT},%
  pdfauthor={David Schneider},
}

@@

\title{Efficiently Handling Guards in the Low Level Design of RPython's Tracing JIT}

@@

The results presented in this section are based on numbers gathered by running
a subset of the standard PyPy benchmarks. The PyPy benchmarks are used to
measure the performance of PyPy and are composed of a series of
micro-benchmarks and larger programs.\footnote{\url{http://speed.pypy.org/}} The
benchmarks were taken from the PyPy benchmarks repository using revision
\texttt{ff7b35837d0f}.\footnote{\url{https://bitbucket.org/pypy/benchmarks/src/ff7b35837d0f}}
The benchmarks were run on a version of PyPy based on the
tag~\texttt{0b77afaafdd0} and patched to collect additional data about the
guards in the machine code
backends.\footnote{\url{https://bitbucket.org/pypy/pypy/src/0b77afaafdd0}} All
benchmark data was collected on a MacBook Pro 64 bit running Max OS 10.8 with
the loop unrolling optimization disabled.\footnote{Since loop unrolling
duplicates the body of loops it would no longer be possible to meaningfully
compare the number of operations before and after optimization. Loop unrolling
is most effective for numeric kernels, so the benchmarks presented here are not
affected much by its absence.}
